Learning to Infer Graphics Programs from Hand-Drawn Images

### 2018-10-18 nips_2018.tex
almost, ready!

We developed a deep network architecture for efficiently inferring a
spec, $S$, from a hand-drawn image, $I$.
Our model combines ideas from
Neurally-Guided Procedural Models~\citep{ritchie2016neurally}
and Attend-Infer-Repeat~\citep{eslami1603attend}, but
we wish to emphasize
that one could use
many different approaches from the computer vision toolkit to
parse an image in to primitive drawing commands  (in our terminology, a ``spec'')~\cite{nsd}.
Our network constructs the
spec one drawing command at a time, conditioned on what it has drawn so far (Fig.~\ref{architecture}).
%When predicting the next drawing
%command, the network takes as input the target image $I$ as well as
%the rendered output of previous drawing commands.
%Intuitively, the network looks at the image it wants to explain, as well as what it has already drawn.  It then decides either to stop drawing or proposes another drawing command to add to the trace set; if it decides to continue drawing, the predicted primitive is rendered to its ``canvas'' and the process repeats.
We first
pass a $256\times 256$ target image and a rendering of the drawing commands so
far (encoded as a two-channel image) to a convolutional network. Given
the features extracted by the convnet, a multilayer perceptron then
predicts a distribution over the next drawing command to execute
(see Tbl.~\ref{drawingCommandTable}).
%We predict the drawing command token-by-token,
%\footnote{Tokens are atomic symbols in the programming language  -- so the model is \emph{not} predicting lines of code character-by-character, but instead the model knows about the syntactic structure of primitive drawing commands}
%%   conditioning each token both on the image
%% features and on the previously generated tokens. 
We also use a
differentiable attention mechanism (Spatial Transformer
Networks:~\cite{jaderberg2015spatial}) to let the model attend to
different regions of the image while predicting drawing commands.
%In Fig.~\ref{architecture} the network first decided to emit the \verb|circle| token
%conditioned on the image features, then it emitted the $x$ coordinate of
%the circle conditioned on the image features and the \verb|circle|
%token, and finally it predicted the $y$ coordinate of the circle
%conditioned on the image features, the \verb|circle| token, and the
%$x$ coordinate.
We currently constrain
coordinates to lie on a discrete $16\times 16$ grid,
but the grid could be made arbitrarily fine.  %% See supplement for the full details
%% of the architecture, which we implemented in
%% Tensorflow~\citep{tensorflow2015-whitepaper}.
%% \remark{There are some more details that are important to provide
%%   about this architecture in the supplement: the
%%   functional form(s) of the probability distributions over tokens, the
%%   network layer sizes, which MLPs share parameters, etc.}

@@

%% For the model in Fig.~\ref{architecture}, the distribution over the next drawing command factorizes as:
%% \begin{equation}
%%   \probability_\theta [t_1t_2\cdots t_K | I,T] = \prod_{k = 1}^K \probability_\theta \left[t_k | a_\theta \left(f_\theta(I,\text{render}(T)) | \{t_j\}_{j = 1}^{k - 1}\right), \{t_j\}_{j = 1}^{k - 1}\right]
%% \end{equation}
%% where $t_1t_2\cdots t_K$ are the tokens in the drawing command, $I$ is
%% the target image, $T$ is a trace set, $\theta$ are the
%% parameters of the neural network, $f_\theta(\cdot,\cdot)$ is the
%% image feature extractor (convolutional network), and $a_\theta(\cdot|\cdot)$ is an attention mechanism. The distribution over
%% traces factorizes as:
%% \begin{equation}
%%   \probability_\theta [T|I] = \prod_{n = 1}^{|T|} \probability_\theta [T_n | I,T_{1:(n-1)}]\times\probability_\theta [\verb|STOP| | I,T]\label{objective}
%% \end{equation}
%% where $|T|$ is the length of trace set $T$, the subscripts
%% on $T$ index drawing commands within the trace (so $T_n$ is a sequence of tokens: $t_1t_2\cdots t_K$), and the \verb|STOP|
%% token is emitted by the network to signal that the trace set
%% explains the image.
We trained our network by sampling specs $S$ and target
images $I$ for randomly generated scenes\footnote{Because rendering ignores ordering  we put the drawing commands into a canonical order}
and maximizing $\probability_\theta[S|I]$,
%Eq.~\ref{objective}
 the likelihood of $S$ given $I$, with respect to
  model parameters $\theta$, by gradient ascent.
We trained on $10^5$ scenes, which takes a day on an Nvidia TitanX GPU.

%% Training does not require backpropagation across the sequence
%% of drawing commands: drawing to the canvas `blocks' the gradients,
%% effectively offloading memory to an external visual store.  
%% This approach is like an autoregressive version of
%% Attend-Infer-Repeat~\citep{eslami1603attend}, but critically, without a learned
%%   recurrent memory state, e.g. an RNN.  We can do without an RNN
%% because we learn from ground truth (image, trace) pairs.  This
%% allows us to handle scenes with many objects without
%% worrying about the conditioning of gradients as they propagate
%% over long sequences, and makes training more straightforward: it
%% is just maximum likelihood estimation of the model parameters.

@@

%A practical application of our neural network is the automatic conversion of hand drawings into a subset of \LaTeX.
 We trained the model
to generalize to hand drawings by introducing noise into the
renderings of the training target images, where the noise process  mimics the kinds of variations found in hand drawings (%% Fig.~\ref{handDrawingExamples}; 
see supplement for details).
While our neurally-guided SMC procedure
used pixel-wise distance as a surrogate for a likelihood function ($L(\cdot|\cdot)$ in Sec.~\ref{neuralNetworkSection}),
 pixel-wise distance fares poorly on hand drawings, which never exactly match
the model's renders.
So, for hand drawings,
we learn a surrogate likelihood function,
$L_{\text{learned}}(\cdot|\cdot)$.
The density $L_{\text{learned}}(\cdot|\cdot)$ is predicted by a convolutional network that we train to predict
the distance between two specs conditioned upon their renderings.
We train $L_{\text{learned}}(\cdot |\cdot )$  to approximate the symmetric difference,
which is  the number of drawing commands by which two specs  differ:
  \begin{equation}
    -\log L_{\text{learned}}(\text{render}(S_1)|\text{render}(S_2))\approx |S_1 - S_2| + |S_2 - S_1|\label{symmetricDistance}
    \end{equation}

@@

Given the DSL and a spec $S$, we want a program that both satisfies $S$
and, at the same time, is the ``best'' explanation of $S$.
For example, we might prefer more general programs or, in the spirit of Occam's razor,
prefer shorter programs.
We wrap these intuitions up into a cost function over programs,
and seek the minimum cost program consistent with $S$:
\begin{equation}
  %  \text{program}(S) = \argmin_{p\in \text{DSL, s.t. }p \text{ consistent w/ } S} \text{cost}(p)\label{programObjective}
    \text{program}(S) = \argmax_{p\in \text{DSL}} \indicator\left[p \text{ consistent w/ } S \right]\exp \left( -\text{cost}(p) \right)\label{programObjective}
\end{equation}
We define the
cost of a program to be the number of Statement's it contains (Tbl.~\ref{DSL}).
We also penalize using many different numerical constants; see supplement.
Returning to the generative model in Fig.~\ref{roadmap},
this setup is the same as saying that the prior probability of a program $p$ is $\propto \exp\left(-\text{cost}(p) \right)$ and the likelihood of a spec $S$ given a program $p$ is $\indicator[p\text{ consistent w/ }S]$.
%\remark{The flow here is a bit off/backwards. ``We want a program that evaluates to $T$ and also minimizes some measure of program cost''---why do we care about cost? It'd be better to start by making a ``Bayesian Occam's razor'' appeal (e.g. the most compact/general program is the more likely explanation) and then saying that one way to do this is to minimize a cost function which is proportional to program length.}

@@

To generate a training corpus for learning a policy,
we synthesized minimum cost programs for each  drawing
and for each $\sigma $,
%Solving these
%\footnote{There are 100 the drawings and $2\times 2\times 2\times 3 = 24$ different values of $\sigma $}
%synthesis problems takes a little over a day on 40 CPUs.
%With the training set in hand we  %This loss is differentiable but nonconvex even if $\pi_{\theta}(\cdot |\cdot )^{-1}$ is convex.
then minimized~\ref{policyLoss} using gradient descent while annealing a softened minimum to the hard minimization equation~\ref{policyLoss}.
%See supplement for details.
Because we want to learn a policy from only $100$ drawings,
we parameterize $\pi$ with a  low-capacity bilinear model with only 96 real-valued parameters; see supplement.
%for $\pi$:
%% \begin{equation}
%%   \pi_{\theta}(\sigma |S)\propto \exp \left( \phi_{\text{params}}(\sigma )^\top\theta \phi_{\text{spec}}(S)\right)
%% \end{equation}
%% where $\phi_{\text{params}}(\sigma  )$ is a one-hot encoding of
%% the parameter settings of $\sigma $ (see Tbl.~\ref{policyOutput})
%% and $\phi_{\text{spec}}(S)$ extracts a few simple features of the trace set $S$;
%% see supplement for details.

\textbf{Experiment 3: Table~\ref{policyEvaluation}; Figure~\ref{policyHistogram}.}
We compare synthesis times for our learned search policy
with 4 alternatives:
 \emph{Sketch}, which poses the
 entire problem wholesale to the Sketch program synthesizer;
 \emph{DC}, a DeepCoder--style model that learns to predict which program components (loops, reflections)
 are likely to be useful~\cite{BalGauBroetal16};
 \emph{End--to-End},
 which trains a recurrent neural network to regress directly from images to programs;
and an \emph{Oracle},
a policy which always picks the quickest to search $\sigma $
 also containing a minimum cost program.
Our approach improves upon Sketch by itself,
and comes close to the Oracle's performance.
One could never construct this Oracle,
because the agent does not know ahead of time which
$\sigma $'s contain minimum cost programs nor does it know how long each
$\sigma $ will take to search.
%The Oracle is an upper bound on the performance of any search policy.
With this learned policy in hand we can synthesize 58\% of programs within a minute.
%
\begin{table}[h]\centering
  \caption{Parameterization of different ways of posing the program synthesis problem. The policy learns to choose parameters likely to quickly yield a minimal cost program.
    %We slightly abuse notation by writing $\sigma $ to mean an assignment to each of these parameters (so $\sigma $ assumes one of 24 different values) and to mean the set of programs selected by that parameterization (so $\sigma \subseteq \text{DSL}$)
  }\label{policyOutput}
  \begin{tabular}{lll}\toprule
  Parameter&Description&Range\\\midrule
  Loops?&Is the program allowed to loop?&$\{\text{True},\text{False}\}$\\
  Reflects?&Is the program allowed to have reflections?&$\{\text{True},\text{False}\}$\\
  Incremental?&Solve the problem piece-by-piece or all at once?&$\{\text{True},\text{False}\}$\\
  Maximum depth& Bound on the depth of the program syntax tree&$\{1,2,3\}$
  \\\bottomrule
  \end{tabular}\vspace{-0.5cm}
  \end{table}
\begin{table}[h]
  \centering
  \begin{minipage}[c]{0.4\textwidth}
  \begin{tabular}{lll}
    \toprule Model&\begin{tabular}{c}
      Median \\search time
    \end{tabular}&\begin{tabular}{c}
      Timeouts\\(1 hr)
      \end{tabular}\\\midrule
    Sketch&274 sec&27\%\\
    DC&187 sec&2\%\\
    End--to--End&63 sec&94\%\\
    Oracle&6 sec&2\%\\
    Ours&28 sec&2\%\\\bottomrule 
    \end{tabular}
  \end{minipage}\hfill%
  \begin{minipage}[c]{0.5\textwidth}
    \caption{Time to synthesize a minimum cost program. Sketch: out-of-the-box performance of Sketch~\citep{solar2008program}. DC: Deep--Coder style baseline that predicts program components, trained like~\cite{BalGauBroetal16}. End--to--End: neural net trained to regress directly from images to programs, which fails to find valid programs 94\% of the time. Oracle:  upper bounds  the performance of any bias--optimal search policy. Ours:  %% $\infty = $ timeout. Red dashed line is median time.
           evaluated w/ 20-fold cross validation.}\label{policyEvaluation}
  \end{minipage}

@@

\subsection{Correcting errors made by the neural network}\label{synthesizerHelpsParsing}
\begin{wrapfigure}{r}{5cm}\vspace{-0.5cm}
  \includegraphics[width = 5cm]{figures/programSuccess7.png}
  \includegraphics[width = 5cm]{figures/programSuccess16.png}
  \caption{Left: hand drawings. Center: interpretations favored by the deep network. Right: interpretations favored after learning a prior over programs. The prior favors  simpler programs, thus (top) continuing the pattern of not having an arrow is preferred, or (bottom) continuing the ``binary search tree'' is preferred.}\label{exampleOfProgramCorrectingMistake}
\vspace{-0.75cm}  \end{wrapfigure}
The program synthesizer corrects errors made by the neural network by favoring specs which lead to more
concise or general programs.  For example, figures with perfectly aligned objects are preferable, %% to figures whose parts are slightly misaligned,
and precise alignment lends itself to short
programs.
Concretely,
we run the program synthesizer on the
Top-$k$  most likely specs output by the neurally guided sampler.
Then, the system
reranks the Top-$k$  by  the prior probability of their programs.
The prior probability of a program is learned by optimizing the parameters of the prior so as to maximize
the likelihood of the ground truth specs;
see supplement for details.
But, this procedure can only correct errors when
a correct spec is in the Top-$k$.
Our sampler could only do better on
7/100 drawings by looking at the Top-100 samples
(see Fig.~\ref{drawingIntersectionOverUnion}),
precluding a statistically significant analysis of how much
learning a prior over programs could help correct errors.
But,
learning this prior does sometimes 
help correct mistakes made by the neural network; %% , and also
%% occasionally introduces mistakes of its own; 
see
Fig.~\ref{exampleOfProgramCorrectingMistake} for a representative
example of the kinds of corrections that it makes.
See supplement for details.

>>>>

We developed a deep network architecture for efficiently inferring a
spec, $S$, from a hand-drawn image, $I$.
Our model combines ideas from
Neurally-Guided Procedural Models~\citep{ritchie2016neurally}
and Attend-Infer-Repeat~\citep{eslami1603attend}, but
we wish to emphasize
that one could use
many different approaches from the computer vision toolkit to
parse an image in to primitive drawing commands  (in our terminology, a ``spec'')~\cite{nsd}.
Our network constructs the
spec one drawing command at a time, conditioned on what it has drawn so far (Fig.~\ref{architecture}).
%When predicting the next drawing
%command, the network takes as input the target image $I$ as well as
%the rendered output of previous drawing commands.
%Intuitively, the network looks at the image it wants to explain, as well as what it has already drawn.  It then decides either to stop drawing or proposes another drawing command to add to the trace set; if it decides to continue drawing, the predicted primitive is rendered to its ``canvas'' and the process repeats.
We first
pass a $256\times 256$ target image and a rendering of the drawing commands so
far (encoded as a two-channel image) to a convolutional network. Given
the features extracted by the convnet, a multilayer perceptron then
predicts a distribution over the next drawing command to execute
(see Tbl.~\ref{drawingCommandTable}).
%We predict the drawing command token-by-token,
%\footnote{Tokens are atomic symbols in the programming language  -- so the model is \emph{not} predicting lines of code character-by-character, but instead the model knows about the syntactic structure of primitive drawing commands}
%%   conditioning each token both on the image
%% features and on the previously generated tokens. 
We also use a
differentiable attention mechanism (Spatial Transformer
Networks:~\cite{jaderberg2015spatial}) to let the model attend to
different regions of the image while predicting drawing commands.
%In Fig.~\ref{architecture} the network first decided to emit the \verb|circle| token
%conditioned on the image features, then it emitted the $x$ coordinate of
%the circle conditioned on the image features and the \verb|circle|
%token, and finally it predicted the $y$ coordinate of the circle
%conditioned on the image features, the \verb|circle| token, and the
%$x$ coordinate.
We currently constrain
coordinates to lie on a discrete $16\times 16$ grid,
but the grid could be made arbitrarily fine.

@@

%% For the model in Fig.~\ref{architecture}, the distribution over the next drawing command factorizes as:
%% \begin{equation}
%%   \probability_\theta [t_1t_2\cdots t_K | I,T] = \prod_{k = 1}^K \probability_\theta \left[t_k | a_\theta \left(f_\theta(I,\text{render}(T)) | \{t_j\}_{j = 1}^{k - 1}\right), \{t_j\}_{j = 1}^{k - 1}\right]
%% \end{equation}
%% where $t_1t_2\cdots t_K$ are the tokens in the drawing command, $I$ is
%% the target image, $T$ is a trace set, $\theta$ are the
%% parameters of the neural network, $f_\theta(\cdot,\cdot)$ is the
%% image feature extractor (convolutional network), and $a_\theta(\cdot|\cdot)$ is an attention mechanism. The distribution over
%% traces factorizes as:
%% \begin{equation}
%%   \probability_\theta [T|I] = \prod_{n = 1}^{|T|} \probability_\theta [T_n | I,T_{1:(n-1)}]\times\probability_\theta [\verb|STOP| | I,T]\label{objective}
%% \end{equation}
%% where $|T|$ is the length of trace set $T$, the subscripts
%% on $T$ index drawing commands within the trace (so $T_n$ is a sequence of tokens: $t_1t_2\cdots t_K$), and the \verb|STOP|
%% token is emitted by the network to signal that the trace set
%% explains the image.
We trained our network by sampling specs $S$ and target
images $I$ for randomly generated scenes\footnote{Because rendering ignores ordering  we put the drawing commands into a canonical order}
and maximizing $\probability_\theta[S|I]$,
%Eq.~\ref{objective}
 the likelihood of $S$ given $I$, with respect to
  model parameters $\theta$, by gradient ascent.
We trained on $10^5$ scenes, which takes a day on an Nvidia TitanX GPU.
Supplement Section 1 gives the full details of the architecture and training of this network.
%% Training does not require backpropagation across the sequence
%% of drawing commands: drawing to the canvas `blocks' the gradients,
%% effectively offloading memory to an external visual store.  
%% This approach is like an autoregressive version of
%% Attend-Infer-Repeat~\citep{eslami1603attend}, but critically, without a learned
%%   recurrent memory state, e.g. an RNN.  We can do without an RNN
%% because we learn from ground truth (image, trace) pairs.  This
%% allows us to handle scenes with many objects without
%% worrying about the conditioning of gradients as they propagate
%% over long sequences, and makes training more straightforward: it
%% is just maximum likelihood estimation of the model parameters.

@@

%A practical application of our neural network is the automatic conversion of hand drawings into a subset of \LaTeX.
 We trained the model
to generalize to hand drawings by introducing noise into the
renderings of the training target images, where the noise process  mimics the kinds of variations found in hand drawings.
While our neurally-guided SMC procedure
used pixel-wise distance as a surrogate for a likelihood function ($L(\cdot|\cdot)$ in Sec.~\ref{neuralNetworkSection}),
 pixel-wise distance fares poorly on hand drawings, which never exactly match
the model's renders.
So, for hand drawings,
we learn a surrogate likelihood function,
$L_{\text{learned}}(\cdot|\cdot)$.
The density $L_{\text{learned}}(\cdot|\cdot)$ is predicted by a convolutional network that we train to predict
the distance between two specs conditioned upon their renderings.
We train $L_{\text{learned}}(\cdot |\cdot )$  to approximate the symmetric difference,
which is  the number of drawing commands by which two specs  differ:
  \begin{equation}
    -\log L_{\text{learned}}(\text{render}(S_1)|\text{render}(S_2))\approx |S_1 - S_2| + |S_2 - S_1|\label{symmetricDistance}
  \end{equation}
Supplement Section 2 explains the architecture and training of $L_{\text{learned}}$.

@@

Given the DSL and a spec $S$, we want a program that both satisfies $S$
and, at the same time, is the ``best'' explanation of $S$.
For example, we might prefer more general programs or, in the spirit of Occam's razor,
prefer shorter programs.
We wrap these intuitions up into a cost function over programs,
and seek the minimum cost program consistent with $S$:
\begin{equation}
  %  \text{program}(S) = \argmin_{p\in \text{DSL, s.t. }p \text{ consistent w/ } S} \text{cost}(p)\label{programObjective}
    \text{program}(S) = \argmax_{p\in \text{DSL}} \indicator\left[p \text{ consistent w/ } S \right]\exp \left( -\text{cost}(p) \right)\label{programObjective}
\end{equation}
We define the
cost of a program to be the number of Statement's it contains (Tbl.~\ref{DSL}).
We also penalize using many different numerical constants; see Supplement Section 3.
Returning to the generative model in Fig.~\ref{roadmap},
this setup is the same as saying that the prior probability of a program $p$ is $\propto \exp\left(-\text{cost}(p) \right)$ and the likelihood of a spec $S$ given a program $p$ is $\indicator[p\text{ consistent w/ }S]$.
%\remark{The flow here is a bit off/backwards. ``We want a program that evaluates to $T$ and also minimizes some measure of program cost''---why do we care about cost? It'd be better to start by making a ``Bayesian Occam's razor'' appeal (e.g. the most compact/general program is the more likely explanation) and then saying that one way to do this is to minimize a cost function which is proportional to program length.}

@@

To generate a training corpus for learning a policy,
we synthesized minimum cost programs for each  drawing
and for each $\sigma $,
%Solving these
%\footnote{There are 100 the drawings and $2\times 2\times 2\times 3 = 24$ different values of $\sigma $}
%synthesis problems takes a little over a day on 40 CPUs.
%With the training set in hand we  %This loss is differentiable but nonconvex even if $\pi_{\theta}(\cdot |\cdot )^{-1}$ is convex.
then minimized~\ref{policyLoss} using gradient descent while annealing a softened minimum to the hard minimization equation~\ref{policyLoss}.
%See supplement for details.
Because we want to learn a policy from only $100$ drawings,
we parameterize $\pi$ with a  low-capacity bilinear model with only 96 real-valued parameters. Supplement Section 4 further details the parameterization and training of the policy.
%for $\pi$:
%% \begin{equation}
%%   \pi_{\theta}(\sigma |S)\propto \exp \left( \phi_{\text{params}}(\sigma )^\top\theta \phi_{\text{spec}}(S)\right)
%% \end{equation}
%% where $\phi_{\text{params}}(\sigma  )$ is a one-hot encoding of
%% the parameter settings of $\sigma $ (see Tbl.~\ref{policyOutput})
%% and $\phi_{\text{spec}}(S)$ extracts a few simple features of the trace set $S$;
%% see supplement for details.

\textbf{Experiment 3: Table~\ref{policyEvaluation}; Figure~\ref{policyHistogram}; Supplement Section 4.}
We compare synthesis times for our learned search policy
with 4 alternatives:
 \emph{Sketch}, which poses the
 entire problem wholesale to the Sketch program synthesizer;
 \emph{DC}, a DeepCoder--style model that learns to predict which program components (loops, reflections)
 are likely to be useful~\cite{BalGauBroetal16};
 \emph{End--to-End},
 which trains a recurrent neural network to regress directly from images to programs;
and an \emph{Oracle},
a policy which always picks the quickest to search $\sigma $
 also containing a minimum cost program.
Our approach improves upon Sketch by itself,
and comes close to the Oracle's performance.
One could never construct this Oracle,
because the agent does not know ahead of time which
$\sigma $'s contain minimum cost programs nor does it know how long each
$\sigma $ will take to search.
%The Oracle is an upper bound on the performance of any search policy.
With this learned policy in hand we can synthesize 58\% of programs within a minute.
%
\begin{table}[h]\centering
  \caption{Parameterization of different ways of posing the program synthesis problem. The policy learns to choose parameters likely to quickly yield a minimal cost program.
    %We slightly abuse notation by writing $\sigma $ to mean an assignment to each of these parameters (so $\sigma $ assumes one of 24 different values) and to mean the set of programs selected by that parameterization (so $\sigma \subseteq \text{DSL}$)
  }\label{policyOutput}
  \begin{tabular}{lll}\toprule
  Parameter&Description&Range\\\midrule
  Loops?&Is the program allowed to loop?&$\{\text{True},\text{False}\}$\\
  Reflects?&Is the program allowed to have reflections?&$\{\text{True},\text{False}\}$\\
  Incremental?&Solve the problem piece-by-piece or all at once?&$\{\text{True},\text{False}\}$\\
  Maximum depth& Bound on the depth of the program syntax tree&$\{1,2,3\}$
  \\\bottomrule
  \end{tabular}\vspace{-0.5cm}
  \end{table}
\begin{table}[h]
  \centering
  \begin{minipage}[c]{0.4\textwidth}
  \begin{tabular}{lll}
    \toprule Model&\begin{tabular}{c}
      Median \\search time
    \end{tabular}&\begin{tabular}{c}
      Timeouts\\(1 hr)
      \end{tabular}\\\midrule
    Sketch&274 sec&27\%\\
    DC&187 sec&2\%\\
    End--to--End&63 sec&94\%\\
    Oracle&6 sec&2\%\\
    Ours&28 sec&2\%\\\bottomrule 
    \end{tabular}
  \end{minipage}\hfill%
  \begin{minipage}[c]{0.5\textwidth}
    \caption{Time to synthesize a minimum cost program. Sketch: out-of-the-box performance of Sketch~\citep{solar2008program}. DC: Deep--Coder style baseline that predicts program components, trained like~\cite{BalGauBroetal16}. End--to--End: neural net trained to regress directly from images to programs, which fails to find valid programs 94\% of the time. Oracle:  upper bounds  the performance of any bias--optimal search policy. Ours:  %% $\infty = $ timeout. Red dashed line is median time.
           evaluated w/ 20-fold cross validation.}\label{policyEvaluation}
  \end{minipage}

@@

\subsection{Correcting errors made by the neural network}\label{synthesizerHelpsParsing}
\begin{wrapfigure}{r}{5cm}\vspace{-0.5cm}
  \includegraphics[width = 5cm]{figures/programSuccess7.png}
  \includegraphics[width = 5cm]{figures/programSuccess16.png}
  \caption{Left: hand drawings. Center: interpretations favored by the deep network. Right: interpretations favored after learning a prior over programs. The prior favors  simpler programs, thus (top) continuing the pattern of not having an arrow is preferred, or (bottom) continuing the ``binary search tree'' is preferred.}\label{exampleOfProgramCorrectingMistake}
\vspace{-0.75cm}  \end{wrapfigure}
The program synthesizer corrects errors made by the neural network by favoring specs which lead to more
concise or general programs.  For example, figures with perfectly aligned objects are preferable, %% to figures whose parts are slightly misaligned,
and precise alignment lends itself to short
programs.
Concretely,
we run the program synthesizer on the
Top-$k$  most likely specs output by the neurally guided sampler.
Then, the system
reranks the Top-$k$  by  the prior probability of their programs.
The prior probability of a program is learned by optimizing the parameters of the prior so as to maximize
the likelihood of the ground truth specs;
see supplement for details.
But, this procedure can only correct errors when
a correct spec is in the Top-$k$.
Our sampler could only do better on
7/100 drawings by looking at the Top-100 samples
(see Fig.~\ref{drawingIntersectionOverUnion}),
precluding a statistically significant analysis of how much
learning a prior over programs could help correct errors.
But,
learning this prior does sometimes 
help correct mistakes made by the neural network; %% , and also
%% occasionally introduces mistakes of its own; 
see
Fig.~\ref{exampleOfProgramCorrectingMistake} for a representative
example of the kinds of corrections that it makes.
See Supplement Section 5 for details.
